Is high social class always beneficial for survival? A study of Northern Sweden 1801--2013

### 2017-10-26 article3.Rmd
Figure titles, corrections

```{r getske4060}
cap1w <-  "Cumulative hazards for social class by time period, ages 40--64, women."
scap1w <-  "Cumulative hazards, ages 40--64, women."
cap1m <-  "Cumulative hazards for social class by time period, ages 40--64, men."
scap1m <-  "Cumulative hazards, ages 40--64, men."
##
cap0 <- "Probability of dying before age 65 for a 40 year old person by social class and decade, women (top) and men (bottom)."
scap0 <- "Probability by social class, ages 40--64."
cap12 <- "Probability of dying before age 65 for a 40 year old person standardised by social class and decade, women (top) and men (bottom)."
scap12 <- "Probability standardised by social class, ages 40--64."
cap12log <- "Probability of dying before age 65 for a 40 year old person by social class and decade, women (top) and men (bottom). The last decades."
scap12log <- "Probability by social class, ages 40--64, last years."

cap2w <-  "Cumulative hazards for social class by time period, ages 65--89, women."
scap2w <-  "Cumulative hazards, ages 65--89, women."
cap2m <-  "Cumulative hazards for social class by time period, ages 65--89, men."
scap2m <-  "Cumulative hazards, ages 65--89, men."
##
cap22 <- "Probability of dying before age 90 for a 65 year old person by social class and decade, women (top) and men (bottom). Standardised."
scap22 <- "Probability by social class, ages 65--89."
cap22log <- "Probability of dying before age 90 for a 65 year old person by HISCLASS and decade, women (top) and men (bottom). The last decades."
scap22log <- "Probability by social class, ages 65--89, last years."

@@

```{r 41getske4060}
cap1w <-  "Cumulative hazards for social class by time period, ages 40--64, women, cardiovascular death."
scap1w <-  "Cumulative hazards, ages 40--64, women, cardiovascular death."
cap1m <-  "Cumulative hazards for social class by time period, ages 40--64, men, cardiovascular death."
scap1m <-  "Cumulative hazards, ages 40--64, men, cardiovascular death."
##
cap12 <- "Total hazard of dying before age 65 for a 40 year old person standardised by social class and decade, women (top) and men (bottom), cardiovascular death."
scap12 <- "Total hazard by social class, ages 40--64, cardiovascular death."
cap12log <- "Total hazard of dying before age 65 for a 40 year old person by social class and decade, women (top) and men (bottom). The last decades, cardiovascular death."
scap12log <- "Total hazard by social class, ages 40--64, last years, cardiovascular death."

cap2w <-  "Cumulative hazards for social class by time period, ages 65--89, women, cardiovascular death."
scap2w <-  "Cumulative hazards, ages 65--89, women, cardiovascular death."
cap2m <-  "Cumulative hazards for social class by time period, ages 65--89, men, cardiovascular death."
scap2m <-  "Cumulative hazards, ages 65--89, men, cardiovascular death."
##
cap22 <- "Total hazard of dying before age 90 for a 65 year old person standardised by social class and decade, women (top) and men (bottom), cardiovascular death."
scap22 <- "Total hazard standardised by social class, ages 65--89, cardiovascular death."
cap22log <- "Total hazard of dying before age 90 for a 65 year old person by social class and decade, women (top) and men (bottom). The last decades, cardiovascular death."
scap22log <- "Total hazard by social class, ages 65--89, last years, cardiovascular death."

@@

```{r 12getske4060}
cap1w <-  "Cumulative hazards for social class by time period, ages 40--64, women, cancer death."
scap1w <-  "Cumulative hazards, ages 40--64, women, cancer death."
cap1m <-  "Cumulative hazards for social class by time period, ages 40--64, men, cancer death."
scap1m <-  "Cumulative hazards, ages 40--64, men, cancer death."
##
cap12 <- "Total hazard of dying before age 65 for a 40 year old person standardised by social class and decade, women (top) and men (bottom), cancer death."
scap12 <- "Total hazard by social class, ages 40--64, cancer death."
cap12log <- "Total hazard of dying before age 65 for a 40 year old person by social class and decade, women (top) and men (bottom). The last decades, cancer death."
scap12log <- "Total hazard by social class, ages 40--64, last years, cancer death."

cap2w <-  "Cumulative hazards for social class by time period, ages 65--89, women, cancer death."
scap2w <-  "Cumulative hazards, ages 65--89, women, cancer death."
cap2m <-  "Cumulative hazards for social class by time period, ages 65--89, men, cancer death."
scap2m <-  "Cumulative hazards, ages 65--89, men, cancer death."
##
cap22 <- "Total hazard of dying before age 90 for a 65 year old person standardised by social class and decade, women (top) and men (bottom), cancer death."
scap22 <- "Total hazard standardised by social class, ages 65--89, cancer death."
cap22log <- "Total hazard of dying before age 90 for a 65 year old person by social class and decade, women (top) and men (bottom). The last decades, cancer death."
scap22log <- "Total hazard by social class, ages 65--89, last years, cancer death."

>>>>

```{r getske4060}
cap1w <-  "Cumulative hazards for social class by time period, ages 40--64, women."
scap1w <-  "Cumulative hazards, ages 40--64, women."
cap1m <-  "Cumulative hazards for social class by time period, ages 40--64, men."
scap1m <-  "Cumulative hazards, ages 40--64, men."
##
cap0 <- "Probability of dying before age 65 for a 40 year old person by social class and period, women (top) and men (bottom)."
scap0 <- "Probability by social class, ages 40--64."
cap12 <- "Probability of dying before age 65 for a 40 year old person standardised by social class and period, women (top) and men (bottom)."
scap12 <- "Probability standardised by social class, ages 40--64."
cap12log <- "Probability of dying before age 65 for a 40 year old person by social class and period, women (top) and men (bottom). The last decades."
scap12log <- "Probability by social class, ages 40--64, last years."

cap2w <-  "Cumulative hazards for social class by time period, ages 65--89, women."
scap2w <-  "Cumulative hazards, ages 65--89, women."
cap2m <-  "Cumulative hazards for social class by time period, ages 65--89, men."
scap2m <-  "Cumulative hazards, ages 65--89, men."
##
cap22 <- "Probability of dying before age 90 for a 65 year old person by social class and period, women (top) and men (bottom). Standardised."
scap22 <- "Probability by social class, ages 65--89."
cap22log <- "Probability of dying before age 90 for a 65 year old person by HISCLASS and period, women (top) and men (bottom). The last decades."
scap22log <- "Probability by social class, ages 65--89, last years."

@@

```{r 41getske4060}
cap1w <-  "Cumulative hazards for social class by time period, ages 40--64, women, cardiovascular death."
scap1w <-  "Cumulative hazards, ages 40--64, women, cardiovascular death."
cap1m <-  "Cumulative hazards for social class by time period, ages 40--64, men, cardiovascular death."
scap1m <-  "Cumulative hazards, ages 40--64, men, cardiovascular death."
##
cap12 <- "Total hazard of dying before age 65 for a 40 year old person standardised by social class and period, women (top) and men (bottom), cardiovascular death."
scap12 <- "Total hazard by social class, ages 40--64, cardiovascular death."
cap12log <- "Total hazard of dying before age 65 for a 40 year old person by social class and period, women (top) and men (bottom). The last decades, cardiovascular death."
scap12log <- "Total hazard by social class, ages 40--64, last years, cardiovascular death."

cap2w <-  "Cumulative hazards for social class by time period, ages 65--89, women, cardiovascular death."
scap2w <-  "Cumulative hazards, ages 65--89, women, cardiovascular death."
cap2m <-  "Cumulative hazards for social class by time period, ages 65--89, men, cardiovascular death."
scap2m <-  "Cumulative hazards, ages 65--89, men, cardiovascular death."
##
cap22 <- "Total hazard of dying before age 90 for a 65 year old person standardised by social class and period, women (top) and men (bottom), cardiovascular death."
scap22 <- "Total hazard standardised by social class, ages 65--89, cardiovascular death."
cap22log <- "Total hazard of dying before age 90 for a 65 year old person by social class and period, women (top) and men (bottom). The last decades, cardiovascular death."
scap22log <- "Total hazard by social class, ages 65--89, last years, cardiovascular death."

@@

```{r 12getske4060}
cap1w <-  "Cumulative hazards for social class by time period, ages 40--64, women, cancer death."
scap1w <-  "Cumulative hazards, ages 40--64, women, cancer death."
cap1m <-  "Cumulative hazards for social class by time period, ages 40--64, men, cancer death."
scap1m <-  "Cumulative hazards, ages 40--64, men, cancer death."
##
cap12 <- "Total hazard of dying before age 65 for a 40 year old person standardised by social class and period, women (top) and men (bottom), cancer death."
scap12 <- "Total hazard by social class, ages 40--64, cancer death."
cap12log <- "Total hazard of dying before age 65 for a 40 year old person by social class and period, women (top) and men (bottom). The last decades, cancer death."
scap12log <- "Total hazard by social class, ages 40--64, last years, cancer death."

cap2w <-  "Cumulative hazards for social class by time period, ages 65--89, women, cancer death."
scap2w <-  "Cumulative hazards, ages 65--89, women, cancer death."
cap2m <-  "Cumulative hazards for social class by time period, ages 65--89, men, cancer death."
scap2m <-  "Cumulative hazards, ages 65--89, men, cancer death."
##
cap22 <- "Total hazard of dying before age 90 for a 65 year old person standardised by social class and period, women (top) and men (bottom), cancer death."
scap22 <- "Total hazard standardised by social class, ages 65--89, cancer death."
cap22log <- "Total hazard of dying before age 90 for a 65 year old person by social class and period, women (top) and men (bottom). The last decades, cancer death."
scap22log <- "Total hazard by social class, ages 65--89, last years, cancer death."
